Type-Safe Modular Parsing

### 2017-01-13 paper/sections/CaseStudy.tex
Text

To demonstrate the utility of our modular parsing approach, we
implemented parsers of the first 18 calculi from book \textit{Types
  and Programming Languages} (TAPL) \cite{pierce2002types}. TAPL introduces several
calculi from simple to complex, by gradually adding new features to
syntax. We compared our implementation with a non-modular implementation
we found online, which is also written in Scala and uses the same Packrat parsing library.
We counted source lines of code (SLOC) and measured execution time for both implementations.
Our implementation saves 69\% code comparing with that non-modular one.

@@

The calculi in the TAPL book are suitable for our case study for mainly two reasons.
Firstly, they capture many of the language features
required in realistic programming languages, such as lambdas, records and variants. Secondly, the evolution of
calculi in the book reveals the advantages of modular representation
of abstract syntax and modular parsing, which is the key functionality
of our approach. By extracting common components from those calculi
and reusing them, we obtain considerably code reuse as shown later.

>>>>

To demonstrate the utility of our modular parsing approach, we
implemented parsers of the first 18 calculi from book \textit{Types and Programming Languages} (TAPL) \cite{pierce2002types}. We compared our implementation with a non-modular implementation
we found online, which is also written in Scala and uses the same Packrat parsing library.
We counted source lines of code (SLOC) and measured execution time for both implementations.
The result suggests that our implementation saves 69\% code comparing with that non-modular one.

@@

TAPL introduces several calculi from simple to complex, by gradually adding new features to syntax. These calculi are suitable for our case study for mainly two reasons. Firstly, they capture many of the language features
required in realistic programming languages, such as lambdas, records and variants. Secondly, the evolution of
calculi in the book reveals the advantages of modular representation
of abstract syntax and modular parsing, which is the key functionality
of our approach. By extracting common components from those calculi
and reusing them, we obtain considerably code reuse as shown later.
